---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---




## Loading and preprocessing the data
```{r loaddata}
library(dplyr)
stepdata <- read.csv("./activity.csv", sep = ",", header = TRUE)
stepdata %>% mutate(stepdata, date=as.Date(date, format = ("%Y-%m-%d")))
```

## What is mean total number of steps taken per day?
```{r stepsday}
dailydata <- stepdata%>%
  group_by(date) %>%
  summarise(total = sum(steps, na.rm = TRUE))
hist(dailydata$total)
```

``` {r meanmedium}
meansteps <- mean(dailydata$total, na.rm = TRUE)
mediansteps <- median(dailydata$total, na.rm = TRUE)
```

The mean number of steps is `r meansteps`.  
The median number of steps is `r mediansteps`

## What is the average daily activity pattern?
```{r stepstime}
intervalmean <- stepdata%>%
  group_by(interval) %>%
  summarise(total = mean(steps, na.rm = TRUE))
  hist(dailydata$total)
```

```{r timeseries}
plot(intervalmean$interval, intervalmean$total, type = "l")
hightime <- intervalmean[which.max(intervalmean$total),]
```

The time of day with most average steps are `r hightime[,1]`

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
